Network Configuration Synthesis with Abstract Topologies

### 2016-11-15 paper/abstraction/paper.tex
add back ratul edits

Routers in the data center network run BGP using private AS numbers and peer with multiple backbone networks. The routers aggregate some prefix blocks when announcing them to the backbone network, and keep some prefixes internal. The policy also ensures that private address space from external neighbors is dropped. The data center prefers that traffic leave through certain peers over others and ensures that transit traffic between peers is dropped.

We use a fat tree topology and scale the size of the topology according the number of pods $k$. The abstract topology uses one abstract node for each tier of the data center with an additional node for separate local and global ToRs.

@@

The backbone policy classifies neighbors into several categories based on commercial relationship and prefers paths through them in order. Similar to the data center, it drops private address space from  neighbors, drops transit traffic between certain peers but not others, and aggregates internal prefixes at the border of the network.

@@

For both networks, the abstract generation starts off slightly slower than Propane's concrete generation for small topologies due to the overhead of the fault-tolerance analysis. However, as the size of the topology increases, abstract generation becomes orders of magnitude faster than concrete generation. In all cases for both networks, abstract generation takes less than 10 seconds to complete.

@@

\sysname compilation strategy guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor. We experimentally confirmed that our implementation provides this guarantee. For the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing prefixes that routers originate. In each case, we found the guarantee to hold; for prefix changes, only the originator's configuration changed. In contrast, all router configurations were modified with Propane because it heavily uses prefix lists which are sensitive to such changes. While Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's underlying structure that \sysname leverages.

>>>>

Routers in the data center network run BGP using unique AS numbers and connect to multiple external neighbors. The routers aggregate some prefix blocks when announcing them to external neighbors, and keep some prefixes internal. The data center prefers that traffic leave through certain neighbors over others and should not transit traffic between neighbors. The policy also says that the data center routers not use external neighbors to reach ``private" destinations  (i.e., those in the part of the IP address space reserved for private use).

We use a fat tree~\cite{fattree} and scale it by increasing the number of pods. The abstract topology uses one abstract node for each tier with additional nodes for local and global ToRs.

@@

The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order. Similar to the datacenter, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.

@@

For both networks, the abstract synthesis is slightly slower than concrete synthesis for small topologies due to the overhead of the fault-tolerance analysis. However, as the topology size increases, abstract synthesis becomes orders of magnitude faster. In all cases for both networks, it takes less than 10 seconds to complete.

@@

\sysname's compilation strategy guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor. We experimentally confirmed that our implementation provides this guarantee. For the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing prefixes that routers originate. In each case, we found the guarantee to hold; for prefix changes, only the originator's configuration changed. In contrast, all router configurations were modified with Propane because it heavily uses prefix lists which are sensitive to such changes. While Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's underlying structure that \sysname leverages.
